    \documentclass[a4paper,10pt]{article}

    % --- TIMES NEW ROMAN & ATS ENCODING ---
    \usepackage[T1]{fontenc}
    \usepackage{times}

    \usepackage[a4paper,margin=0.30in]{geometry}
    \usepackage{enumitem}
    \usepackage{titlesec}
    \usepackage[hidelinks]{hyperref}

    % Clean, tight spacing for section headings
    \titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
    \titlespacing*{\section}{0pt}{5pt}{3pt}

    % Globally reduce itemize vertical heights (pointers height reduction)
    \setlist[itemize]{
        noitemsep,
        topsep=1pt,
        parsep=0pt,
        partopsep=0pt,
        itemsep=1.5pt
    }

    \setlength{\parindent}{0pt}

    \begin{document}
    \pagestyle{empty}

    \begin{center}
        {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
        Frontend Developer - RAG \& AI/LLM Specialist\\[4pt]
        +91-7620876612 \quad
        \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
        \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
        \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
    \end{center}

    \section*{Summary}

    Frontend Software Engineer with 1+ year of experience specializing in RAG (Retrieval-Augmented Generation) systems, embeddings, and AI-powered web applications. Expert in building React.js and Next.js applications integrated with vector databases, semantic search, and LLM workflows. Proficient in prompt engineering, evaluating AI outputs using structured metrics, and context retrieval techniques. Focused on delivering high-performance, maintainable user interfaces for intelligent document processing and knowledge-based systems.

    \section*{Skills}

    \textbf{Frontend:} JavaScript (ES6+), TypeScript, React.js, Next.js, Redux Toolkit, GSAP, Framer Motion, Tailwind CSS, ShadCN, HTML5, CSS3\\
    \textbf{RAG \& AI/LLM Technologies:} Retrieval-Augmented Generation (RAG), Embeddings for Semantic Search, Vector Databases (Pinecone, Weaviate, Chroma), Prompt Engineering Techniques, LLM Integration, AI Output Evaluation, Structured Metrics \& Feedback, Context Retrieval Workflows\\
    \textbf{Backend \& APIs:} Node.js, Express.js, REST APIs, JWT Authentication, RBAC\\
    \textbf{Databases:} PostgreSQL, MongoDB, Vector Databases, DBMS\\
    \textbf{Programming \& CS Fundamentals:} Python, TypeScript, Data Structures \& Algorithms, System Design, Computer Networking\\
    \textbf{Tools \& Platforms:} AWS EC2, Git, Linux, Postman, Nginx

    \section*{Experience}

    \textbf{Software Developer - RAG \& AI Systems} \hfill May 2025 -- Present\\
    Sitramix, Pune\\
    \textit{Tools Used: React.js, TypeScript, Node.js, Vector Databases, RAG Systems}

    
\begin{itemize}[leftmargin=*]
    \item Built scalable React.js frontend features with RAG integration, semantic search capabilities, and intelligent context retrieval for knowledge-based systems.
    
    \item Developed reusable frontend components for embedding visualization and AI output evaluation dashboards using structured metrics and feedback loops.
    
    \item Implemented vector database workflows (Pinecone, Weaviate, Chroma) for semantic search and context retrieval, improving application intelligence and user experience.
    
    \item Integrated LLM-powered features with prompt engineering techniques, enabling dynamic and responsive AI-assisted user interfaces.
    
    \item Designed and optimized embedding-based search functionality for document processing, significantly improving content discoverability and relevance ranking.
    
    \item Improved frontend performance and SEO for AI-powered applications, maintaining Lighthouse scores of 90+ across core web metrics.
    
    \item Collaborated with backend engineers to design efficient RAG pipelines, optimizing context retrieval and LLM response quality.
    
    \item Evaluated and refined AI outputs using structured metrics, user feedback, and iterative refinement techniques to ensure production-grade quality.
\end{itemize}


    \section*{Projects}

\textbf{Griffion -- Authentication Starter Kit | Next.js, Node.js, MongoDB, JWT}

\begin{itemize}[leftmargin=*]
    \item Built a reusable authentication starter kit providing pre-configured frontend and backend architecture for rapid application development.
    
    \item Implemented complete authentication workflows including JWT rotation, refresh token handling, RBAC, protected routes, and session management.
    
    \item Reduced repetitive setup effort by providing production-ready authentication infrastructure, enabling developers to focus primarily on business logic and UI development.
\end{itemize}

\textbf{JobJet -- Job Portal Platform | React.js, Tailwind CSS, Node.js, Express.js}

\begin{itemize}[leftmargin=*]
    \item Built a full-stack job portal platform supporting job listings, application workflows, user authentication, and recruiter-candidate interactions.
    
    \item Developed responsive frontend interfaces with structured state management and REST API integration for jobs, applications, and user workflows.
    
    \item Designed backend APIs with authentication, file uploads, validation, and role-based access handling using Node.js and Express.js.
\end{itemize}

\textbf{TICKETIFY -- Event Management Platform | React Native, Node.js}

\begin{itemize}[leftmargin=*]
    \item Built a cross-platform event management application supporting ticket booking, attendee management, and real-time event workflows.
    
    \item Implemented QR-based ticket validation and real-time attendee synchronization for faster and more reliable event check-in operations.
    
    \item Developed reusable mobile UI components and backend APIs to support scalable ticketing and event management workflows.
\end{itemize}
    \section*{Awards \& Certifications}

    \begin{itemize}[leftmargin=*]
        \item Secured 1st Rank in college during Bachelor's degree graduation (BBA-CA / BCA) with an outstanding CGPA of 9.60/10.
    \end{itemize}

    \section*{Education}

    \textbf{Master of Computer Applications (MCA)} \hfill Expected: June 2027\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 8.96 

    \vspace{4pt} 

    \textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 9.60 / 10

    \vspace{4pt} 

    \textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022\\
    A.S.D.B. Dadawala Junior College\\
    Percentage: 87.50\%

    \vspace{4pt} 

    \textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020\\
    V.P.S. Sheth Hiralal Saraf Prashala (S.H.S.P.)\\
    Percentage: 88.20\%

    \end{document}