    \documentclass[a4paper,10pt]{article}

    % --- TIMES NEW ROMAN & ATS ENCODING ---
    \usepackage[T1]{fontenc}
    \usepackage{times}

    \usepackage[a4paper,margin=0.30in]{geometry}
    \usepackage{enumitem}
    \usepackage{titlesec}
    \usepackage[hidelinks]{hyperref}

    % Clean, tight spacing for section headings
    \titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
    \titlespacing*{\section}{0pt}{5pt}{3pt}

    % Globally reduce itemize vertical heights (pointers height reduction)
    \setlist[itemize]{
        noitemsep,
        topsep=1pt,
        parsep=0pt,
        partopsep=0pt,
        itemsep=1.5pt
    }

    \setlength{\parindent}{0pt}

    \begin{document}
    \pagestyle{empty}

    \begin{center}
        {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
        Frontend Software Developer\\[4pt]
        +91-7620876612 \quad
        \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
        \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
        \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
    \end{center}

    \section*{Summary}

    Frontend-focused Software Engineer with 1+ year of experience building React.js and Next.js applications with emphasis on performance, reusable component architecture, and scalable frontend development. Experienced in REST API integration, state management, and delivering production-ready user interfaces across web applications. Possesses working knowledge of backend systems, databases, and core computer science fundamentals.

    \section*{Skills}

    \textbf{Frontend:} JavaScript (ES6+), React.js, Next.js, Redux Toolkit, GSAP, Framer Motion, Tailwind CSS, ShadCN, HTML5, CSS3\\
    \textbf{Backend \& APIs:} Node.js, Express.js, REST APIs, JWT Authentication, RBAC\\
    \textbf{Databases:} PostgreSQL, MongoDB,DBMS\\
    \textbf{Programming \& CS Fundamentals:} Python, Data Structures \& Algorithms, System Design, Computer Networking\\
    \textbf{Tools \& Platforms:} AWS EC2, Git, Linux, Postman, Nginx

    \section*{Experience}

    \textbf{Software Developer} \hfill May 2025 -- Present\\
    Sitramix, Pune\\
    \textit{Tools Used: React.js, Node.js, Express.js, JWT, AWS}

    
\begin{itemize}[leftmargin=*]
    \item Built scalable React.js frontend features with reusable component architecture and structured state management across multiple modules.
    
    \item Developed reusable frontend systems that replaced a manual design-to-development workflow, reducing implementation time by approximately 90\%.
    
    \item Improved frontend performance, accessibility, and SEO, achieving Lighthouse scores of 90+ across core web metrics.
    \item Integrated and maintained REST API workflows with structured asynchronous handling, loading states, and error management.
    
    \item Designed and developed RESTful APIs using Node.js and Express.js with authentication and role-based access control.
    
    \item Improved backend response reliability by optimizing database queries and API handling.
    
    \item Deployed and monitored applications on AWS, contributing to production stability and application performance.
\end{itemize}


    \section*{Projects}

\textbf{Griffion -- Authentication Starter Kit | Next.js, Node.js, MongoDB, JWT}

\begin{itemize}[leftmargin=*]
    \item Built a reusable authentication starter kit providing pre-configured frontend and backend architecture for rapid application development.
    
    \item Implemented complete authentication workflows including JWT rotation, refresh token handling, RBAC, protected routes, and session management.
    
    \item Reduced repetitive setup effort by providing production-ready authentication infrastructure, enabling developers to focus primarily on business logic and UI development.
\end{itemize}

\textbf{JobJet -- Job Portal Platform | React.js, Tailwind CSS, Node.js, Express.js}

\begin{itemize}[leftmargin=*]
    \item Built a full-stack job portal platform supporting job listings, application workflows, user authentication, and recruiter-candidate interactions.
    
    \item Developed responsive frontend interfaces with structured state management and REST API integration for jobs, applications, and user workflows.
    
    \item Designed backend APIs with authentication, file uploads, validation, and role-based access handling using Node.js and Express.js.
\end{itemize}

\textbf{TICKETIFY -- Event Management Platform | React Native, Node.js}

\begin{itemize}[leftmargin=*]
    \item Built a cross-platform event management application supporting ticket booking, attendee management, and real-time event workflows.
    
    \item Implemented QR-based ticket validation and real-time attendee synchronization for faster and more reliable event check-in operations.
    
    \item Developed reusable mobile UI components and backend APIs to support scalable ticketing and event management workflows.
\end{itemize}
    \section*{Awards \& Certifications}

    \begin{itemize}[leftmargin=*]
        \item Secured 1st Rank in college during Bachelor's degree graduation (BBA-CA / BCA) with an outstanding CGPA of 9.60/10.
    \end{itemize}

    \section*{Education}

    \textbf{Master of Computer Applications (MCA)} \hfill Expected: June 2027\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 8.96 

    \vspace{4pt} 

    \textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 9.60 / 10

    \vspace{4pt} 

    \textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022\\
    A.S.D.B. Dadawala Junior College\\
    Percentage: 87.50\%

    \vspace{4pt} 

    \textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020\\
    V.P.S. Sheth Hiralal Saraf Prashala (S.H.S.P.)\\
    Percentage: 88.20\%

    \end{document}