\documentclass[a4paper,10pt]{article}

% --- TIMES NEW ROMAN & ATS ENCODING ---
\usepackage[T1]{fontenc}
\usepackage{times}

\usepackage[a4paper,margin=0.40in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}

% Clean, tight spacing for section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{4pt}

% Globally reduce itemize vertical heights (pointers height reduction)
\setlist[itemize]{
    noitemsep,
    topsep=1pt,
    parsep=0pt,
    partopsep=0pt,
    itemsep=1.5pt
}

\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}

% HEADER
\begin{minipage}[t]{0.75\textwidth}
    {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\[4pt]
    {\Large \textbf{Software Developer}}\\[6pt]
    \textbf{Phone:} +91-7620876612\\
    \textbf{Email:} \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com}\\[4pt]
    \textbf{Links \& Profiles:}\\
    \href{https://shivsarwade.vercel.app/}{shivsarwade.vercel.app} (Portfolio)\\
    \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} (LinkedIn)\\
    \href{https://github.com/ShivSarwade}{github.com/ShivSarwade} (GitHub)\\
\end{minipage}%
\begin{minipage}[t]{0.25\textwidth}
    \vspace{-10pt}
    \raggedleft
    \framebox[3cm]{\rule{0pt}{3.5cm} \textit{Passport Photo}}
\end{minipage}

\vspace{5pt}

\section*{Summary}
Software Development Engineer with hands-on experience building scalable distributed systems, optimizing API latency, and designing robust full-stack workflows. Proficient in Data Structures \& Algorithms, object-oriented design, and system architecture. Proven track record of independently shipping production-ready web applications, resolving performance bottlenecks, and driving end-to-end product development. Adept at cross-functional collaboration and rapidly adapting to new technologies to deliver high-quality software solutions in agile environments.

\section*{Technical Skills}
\textbf{Skilled:}\\[2pt]
Node.js, Express.js, React.js, Next.js, RESTful APIs, JavaScript (ES6+), MongoDB, PostgreSQL 

\vspace{4pt}
\textbf{Intermediate:}\\[2pt]
Python, Java, SQL, AWS, Git, Linux 

\vspace{4pt}
\textbf{Basic:}\\[2pt]
Redis, Nginx, Docker, RAG, LangGraph, Vercel, Supabase,

\section*{Projects}

\textbf{Griffion -- Identity \& Authentication Service}\\
\textbf{Synopsis:} Developed a modular authentication microservice serving as the core identity provider for internal tools. My personal contribution involved architecting the backend systems, building secure REST APIs, designing database schemas, and setting up protected frontend routing using \textbf{Node.js, React.js, MongoDB, Redis, and JWT}. \textbf{Challenge \& Independent Research:} A major challenge was high authorization latency under concurrent requests. Through independent research into database optimization and caching layers, I implemented efficient indexing and Redis caching strategies, successfully reducing query overhead and authorization latency by 30\%.

\vspace{6pt}

\textbf{JobJet -- Full-Stack Job Portal}\\
\textbf{Synopsis:} Engineered a scalable job-matching platform facilitating seamless recruiter-candidate interactions. I solely developed the backend infrastructure for application tracking, secure resume uploads, and user profile management, along with building a responsive component-driven frontend using \textbf{Python, React.js, Node.js, PostgreSQL, and Tailwind CSS}. \textbf{Challenge \& Independent Research:} A significant challenge was matching candidates to jobs from large datasets efficiently. I solved this by independently researching and implementing an optimized string search and sorting algorithm in Python to handle the data load effectively.

\vspace{6pt}

\textbf{TICKETIFY -- Event Management System}\\
\textbf{Synopsis:} Engineered a cross-platform event application backend supporting high-concurrency ticket booking and real-time attendee synchronization. My contribution focused on creating highly available REST APIs and implementing secure QR-based ticket validation for reliable check-ins using \textbf{React Native, Node.js, and MongoDB}. \textbf{Challenge \& Independent Research:} I faced challenges handling high concurrency under heavy load during ticket sales. I addressed this by independently researching distributed system patterns and implementing fault-tolerant asynchronous services to prevent system bottlenecks.

\section*{Experience}
\textbf{Software Developer} $|$ \textit{Sitramix, Pune} \hfill May 2025 -- Present\\
Architected scalable full-stack features, optimized RESTful API endpoints reducing response time by 40\%, and implemented robust JWT/RBAC security. Shipped 4 projects till now and contributed to making frontend pages in production. Also worked on deployment on AWS EC2 and S3 to ensure 99.9\% uptime.

\vspace{6pt}

\textbf{GCC Social Member} $|$ \textit{Garware College of Commerce} \hfill August 2023 -- May 2025 (2 Years)\\
Managed social media operations for 2 years as part of membership certification.

\vspace{6pt}

\textbf{Digital Marketing Intern} $|$ \textit{Drive} \hfill April 2024 -- June 2024\\
Contributed to digital marketing campaigns, focusing on user engagement, audience targeting, and content strategy.

\section*{Education}
\textbf{Master of Computer Applications (MCA)} $|$ \textit{Savitribai Phule Pune University} \hfill Expected: June 2027 \quad \textbf{CGPA: 8.93} \textbf{(81.80\%)}

\vspace{4pt} 

\textbf{Bachelor of Business Administration in Computer Applications (BCA)} $|$ \textit{SPPU} \hfill Graduated: 2025 \quad \textbf{CGPA: 9.60 / 10} \textbf{(92\%)}

\vspace{4pt} 

\textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022 \quad \textbf{Percentage: 87.50\%}

\vspace{4pt} 

\textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020 \quad \textbf{Percentage: 88.20\%}

\end{document}
