\documentclass[a4paper,10pt]{article}

% --- TIMES NEW ROMAN & ATS ENCODING ---
\usepackage[T1]{fontenc}
\usepackage{times}

\usepackage[a4paper,margin=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% Clean, tight spacing for section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Globally reduce itemize vertical heights (pointers height reduction)
\setlist[itemize]{
    noitemsep,
    topsep=1pt,
    parsep=0pt,
    partopsep=0pt,
    itemsep=1.5pt
}

\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
    Software Developer\\[4pt]
    +91-7620876612 \quad
    \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
    \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
    \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
\end{center}

\section*{Summary}

Software Developer with hands-on experience building scalable backend systems, optimizing API latency, and designing robust data workflows. Proficient in computer science fundamentals and Data Structures \& Algorithms (DSA) in Python. Experienced in writing clean, object-oriented code, designing database schemas, and working under agile environments to solve ambiguous engineering problems. Foundational knowledge of Python and Java, with strong hands-on expertise in Node.js, Express.js, MongoDB, and PostgreSQL.

\section*{Skills}

\textbf{Programming Languages:} Python (Basic/DSA), Java (Basic), JavaScript (ES6+), SQL\\
\textbf{Core CS \& Algorithms:} Data Structures \& Algorithms (DSA) in Python, Object-Oriented Design (OOD), Complexity Analysis (Big-O)\\
\textbf{Backend Technologies:} Node.js, Express.js, REST APIs, JWT Authentication, RBAC, API Validation, Middleware\\
\textbf{Databases \& Cloud:} PostgreSQL, MongoDB, AWS, Nginx\\
\textbf{Tools \& Platforms:} Git, GitHub, Linux, Docker, Postman\\
\textbf{Methodologies:} Agile/Scrum, Software Development Life Cycle (SDLC), Code Reviews

\section*{Experience}

\textbf{Software Developer} \hfill May 2025 -- Present\\
Sitramix, Pune\\
\textit{Tools Used: Node.js, Express.js, React.js, Next.js, MongoDB, PostgreSQL, AWS}

\begin{itemize}[leftmargin=*]
    \item Designed and optimized 20+ secure RESTful API endpoints, improving scalability for distributed backend operations.
    \item Implemented low-latency JWT-based authentication and Role-Based Access Control (RBAC) to secure multi-role workflows.
    \item Optimized PostgreSQL (indexing) and MongoDB queries, improving execution latency and resource utilization.
    \item Leveraged React/Next.js and state memoization to reduce unnecessary frontend re-renders by 25--35\%.
    \item Integrated 15+ asynchronous APIs with robust error-handling and fault-tolerant state management.
    \item Supported AWS deployments and production debugging, ensuring runtime stability and application uptime.
    \item Collaborated in agile teams to design robust solutions for ambiguous technical requirements.
\end{itemize}

\section*{Projects}

\textbf{Algorithmic Solutions \& Data Structures | Python, Git}

\begin{itemize}[leftmargin=*]
    \item Implemented 100+ optimized Data Structures \& Algorithms (Trees, Graphs, DP, Search) in Python.
    \item Analyzed and optimized time and space complexity (Big-O) to ensure maximum execution efficiency.
    \item Authored clean, object-oriented (OOP) Python code adhering to strict software engineering standards.
\end{itemize}

\textbf{Griffion -- Security \& Authentication Platform | Node.js, React.js, MongoDB}

\begin{itemize}[leftmargin=*]
    \item Developed modular security architecture featuring JWT rotation, refresh tokens, and RBAC.
    \item Optimized MongoDB schemas to minimize query overhead and improve authorization latency.
    \item Built robust backend REST APIs and secure frontend workflows with protected routing.
\end{itemize}

\textbf{JobJet -- Job Portal Platform | Python, React.js, Node.js, MongoDB}

\begin{itemize}[leftmargin=*]
    \item Engineered a Python-based job-matching service with optimized string search and sorting algorithms.
    \item Designed responsive UI states and structured API payloads using React.js and Tailwind CSS.
    \item Created backend REST APIs for application tracking, user authentication, and profile management.
\end{itemize}

\section*{Awards \& Certifications}

\begin{itemize}[leftmargin=*]
    \item Secured 1st Rank in college during Bachelor's degree graduation (BBA-CA / BCA) with an outstanding CGPA of 9.60/10.
\end{itemize}

\section*{Education}

\textbf{Master of Computer Applications (MCA)} \hfill Expected: June 2027\\
Savitribai Phule Pune University (SPPU)\\
CGPA: 8.96 

\vspace{4pt} 

\textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
Savitribai Phule Pune University (SPPU)\\
CGPA: 9.60 / 10

\end{document}