\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

% Set font to sans-serif for a modern look (optional, can be removed)
\renewcommand{\familydefault}{\sfdefault}

% Hide page numbers
\pagestyle{empty}

% Command to add vertical space without paragraph indentation
\newcommand{\mypar}{\vspace{1em}\noindent}

\begin{document}

\begin{flushleft}
\textbf{\Large Shiv Sarwade}\\[0.5em]
Frontend \& Full Stack Developer\\[0.5em]
+91-7620876612 | \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} | \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade}
\vspace{2em}

Dear Hiring Team,\mypar

I have attached my assignment submission and prototype for your review.\mypar

I would like to briefly explain why I believe I can be a strong addition to SRV Media.\mypar

While many frontend developers focus only on building interfaces, my skill set extends across modern web engineering, cloud deployment, AI integrations, and digital marketing. This allows me to contribute not only to development but also to business outcomes.\mypar

My frontend expertise includes React.js, Next.js, Tailwind CSS, GSAP, Framer Motion, responsive UI architecture, performance optimization, accessibility, and modern component-driven development. I enjoy building websites that are not only visually appealing but also fast, scalable, and conversion-focused.\mypar

Beyond frontend development, I have hands-on experience with AWS, Vercel deployments, backend integrations, REST APIs, authentication systems, databases, and full-stack application architecture. This enables me to work efficiently across multiple layers of a product without depending heavily on separate teams.\mypar

I also actively work with AI-powered systems including Python, LLM integrations, RAG (Retrieval-Augmented Generation), AI workflows, automation pipelines, and intelligent business solutions. As AI becomes increasingly important in digital products, I can help bridge the gap between traditional web applications and next-generation AI experiences.\mypar

Another advantage I bring is my understanding of digital marketing. Unlike many developers who focus purely on code, I understand user acquisition, landing page optimization, performance metrics, customer journeys, SEO considerations, and conversion-focused design. For an agency like SRV Media, where technology and marketing often intersect, this perspective can create additional value.\mypar

I may not have the longest number of years in the industry, but I consistently compensate through rapid learning, strong execution speed, adaptability, and an AI-first development workflow that allows me to ship quality work efficiently.\mypar

My objective is simple: build products that perform well technically, look exceptional, and contribute measurable business value.\mypar

Thank you for considering my application. I appreciate the opportunity and look forward to discussing how I can contribute to SRV Media.\mypar

Sincerely,\\[1em]
Shiv Sarwade\\
Frontend \& Full Stack Developer

\end{flushleft}
\end{document}
