\documentclass[a4paper,10pt]{article}

% --- TIMES NEW ROMAN & ATS ENCODING ---
\usepackage[T1]{fontenc}
\usepackage{times}

\usepackage[a4paper,margin=0.30in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% Clean, tight spacing for section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Globally reduce itemize vertical heights (pointers height reduction)
\setlist[itemize]{
    noitemsep,
    topsep=1pt,
    parsep=0pt,
    partopsep=0pt,
    itemsep=1.5pt
}

\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
    Frontend \& Full Stack Developer\\[4pt]
    +91-7620876612 \quad
    \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
    \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
    \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
\end{center}

\section*{Summary}

Frontend \& Full Stack Developer with expertise in building scalable, visually appealing, and conversion-focused web applications. Proficient in React.js, Next.js, Tailwind CSS, GSAP, and modern component-driven development. Experienced in integrating AI workflows (LLMs, RAG), optimizing performance, and building full-stack applications with Node.js and AWS. Brings a unique blend of technical expertise and digital marketing knowledge, understanding user acquisition, SEO, and business outcomes.

\section*{Skills}

\textbf{Frontend Technologies:} React.js, Next.js, Redux Toolkit, Tailwind CSS, GSAP, Framer Motion, HTML5, CSS3, Responsive UI\\
\textbf{Backend \& Cloud:} Node.js, Express.js, RESTful APIs, PostgreSQL, MongoDB, AWS (EC2, Vercel), Nginx\\
\textbf{AI \& Languages:} JavaScript (ES6+), Python, AI Integrations, LLMs, RAG, Java, SQL, C++\\
\textbf{Marketing \& Growth:} Digital Marketing, SEO, User Acquisition, Performance Metrics, Landing Page Optimization

\section*{Experience}

\textbf{Software Developer} \hfill May 2025 -- Present\\
Sitramix, Pune\\
\textit{Tools Used: React.js, Next.js, Node.js, Tailwind CSS, MongoDB, PostgreSQL, AWS}

\begin{itemize}[leftmargin=*]
    \item Architected and developed scalable frontend features using React.js and Next.js, implementing state memoization to reduce unnecessary component re-renders by 35\%.
    \item Designed responsive UI architectures and modern component-driven workflows, focusing on performance optimization and accessibility.
    \item Developed and optimized secure RESTful API endpoints, reducing backend response time by 40\% to ensure smooth frontend data integration.
    \item Implemented JWT-based authentication and Role-Based Access Control (RBAC) to secure multi-tenant workflows.
    \item Managed AWS EC2 and Vercel deployments, ensuring high availability and robust performance for full-stack applications.
\end{itemize}

\textbf{Digital Marketing Intern} \hfill April 2024 -- June 2024\\
MES Garware College of Commerce, Pune

\begin{itemize}[leftmargin=*]
    \item Contributed to digital marketing campaigns, focusing on user engagement, audience targeting, and content strategy for 3 months.
    \item Analyzed performance metrics to optimize outreach, integrating marketing perspectives into digital workflows.
    \item Collaborated with the marketing team to align technical tools with user acquisition goals.
\end{itemize}

\textbf{Social Team Member} \hfill August 2022 -- May 2024\\
MES Garware College of Commerce, Pune

\begin{itemize}[leftmargin=*]
    \item Actively served as a Social Team Member for 2 years, organizing and managing events to enhance student engagement and community outreach.
    \item Led promotional initiatives and managed social presence, improving communication and participation across the campus.
\end{itemize}

\section*{Projects}

\textbf{Griffion -- Identity \& Authentication Service | Node.js, React.js, MongoDB}

\begin{itemize}[leftmargin=*]
    \item Built secure frontend workflows with protected routing, accelerating time-to-market for new internal tools.
    \item Developed a modular authentication microservice featuring JWT rotation, refresh token mechanisms, and secure session management.
\end{itemize}

\textbf{JobJet -- Full-Stack Job Portal | Python, React.js, Node.js, PostgreSQL}

\begin{itemize}[leftmargin=*]
    \item Designed a responsive, component-driven frontend architecture using React.js and Tailwind CSS for seamless recruiter-candidate interactions.
    \item Engineered a scalable job-matching engine using Python, and created backend REST APIs using Node.js for tracking and resume uploads.
\end{itemize}

\section*{Awards \& Certifications}

\begin{itemize}[leftmargin=*]
    \item Secured 1st Rank in college during Bachelor's degree graduation (BBA-CA / BCA) with an outstanding CGPA of 9.60/10.
\end{itemize}

\section*{Education}

\textbf{Master of Computer Applications (MCA)} \hfill Expected: June 2027\\
Savitribai Phule Pune University (SPPU)\\
CGPA: 8.96 

\vspace{4pt} 

\textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
MES Garware College of Commerce, Pune\\
CGPA: 9.60 / 10

\vspace{4pt} 

\textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022\\
Percentage: 87.50\%

\vspace{4pt} 

\textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020\\
Percentage: 88.20\%

\end{document}
