\documentclass[a4paper,10pt]{article}

% --- TIMES NEW ROMAN & ATS ENCODING ---
\usepackage[T1]{fontenc}
\usepackage{times}

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
    Software Developer\\[4pt]
    +91-7620876612 \quad
    \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
    \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
    \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
\end{center}

\vspace{2em}

\today

\textbf{Hiring Team}\\
Mastercard\\
\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer II position at Mastercard. With over a year of hands-on experience building scalable, secure full-stack applications and a solid foundation in computer science and software engineering methodologies, I am eager to contribute to Mastercard's mission of powering economies and building a sustainable, secure digital payment ecosystem.

In my current role as a Software Developer at Sitramix, I have successfully managed the end-to-end software development lifecycle, aligning closely with the core accountabilities outlined in your job description. I have designed and optimized over 20 secure RESTful API endpoints and implemented low-latency JWT-based authentication and Role-Based Access Control (RBAC). Security and data confidentiality are paramount in my work, reflecting Mastercard's strict corporate security responsibilities. Furthermore, my experience in optimizing complex PostgreSQL and MongoDB queries has directly improved execution latency and resource utilization for high-traffic data workflows.

Your requirement for a proactive engineer who can perform feasibility studies, logic designs, and analyze input-output flows resonates strongly with my daily responsibilities. I am highly accustomed to working in agile, matrix-based project teams where I actively document software programs following strict QA/QC standards and resolve production bottlenecks to maintain 99.9\% application uptime. My projects, such as the Griffion Security \& Authentication Platform, demonstrate my ability to research and evaluate technical solution alternatives—minimizing query overhead and improving authorization latency. 

I am highly detail-oriented, self-motivated, and thrive in dynamic environments where continuous process improvement and stringent security standards are prioritized. I would welcome the opportunity to bring my technical expertise in Node.js, React.js, and database optimization, as well as my collaborative team spirit, to Mastercard. 

Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with the goals of your engineering team.

Sincerely,

\vspace{1em}
\textbf{Shiv Santosh Sarwade}

\end{document}
