\documentclass[a4paper,10pt]{article}

% --- TIMES NEW ROMAN & ATS ENCODING ---
\usepackage[T1]{fontenc}
\usepackage{times}

\usepackage[a4paper,margin=0.30in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% Clean, tight spacing for section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Globally reduce itemize vertical heights (pointers height reduction)
\setlist[itemize]{
    noitemsep,
    topsep=1pt,
    parsep=0pt,
    partopsep=0pt,
    itemsep=1.5pt
}

\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
    Software Engineer \\[4pt]
    +91-7620876612 \quad
    \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
    \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
    \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
\end{center}
\section*{Summary}

Software Engineer with hands-on experience building scalable full-stack applications and backend systems using Node.js, React.js, PostgreSQL, and MongoDB. Skilled in API development, authentication systems, database optimization, cloud deployment, and performance-focused application development. Experienced in designing secure software solutions, improving system reliability, and working across complete software development lifecycles in agile engineering environments.


\section*{Skills}

\textbf{Languages \& Core CS:} JavaScript (ES6+), Python, Java, SQL, Data Structures \& Algorithms, Object-Oriented Programming, System Design\

\textbf{Backend Engineering:} Node.js, Express.js, REST APIs, Authentication, JWT, RBAC, API Design\

\textbf{Frontend Technologies:} React.js, Next.js, Redux Toolkit, React Native, Tailwind CSS, HTML5, CSS3\

\textbf{Databases \& Cloud:} PostgreSQL, MongoDB, AWS (EC2, S3), Redis, Nginx\

\textbf{Tools \& Methodologies:} Git, Linux, Docker, Postman, CI/CD, Agile/Scrum, SDLC, Debugging


\section*{Experience}

\textbf{Software Developer} \hfill May 2025 -- Present\\
Sitramix, Pune\\
\textit{Tools Used: Node.js, Express.js, React.js, Next.js, MongoDB, PostgreSQL, AWS, Docker}

\begin{itemize}[leftmargin=*]

\item Developed scalable full-stack features across frontend, backend, database, and deployment workflows.
\item Designed and optimized 20+ secure RESTful API endpoints, reducing API response time by 40\% through caching and payload optimization.
\item Optimized PostgreSQL and MongoDB queries, improving execution latency and resource utilization for high-traffic workflows.
\item Leveraged React.js and Next.js to reduce unnecessary component re-renders by 35\% through state optimization and memoization.
\item Implemented asynchronous backend services with robust error handling to improve reliability and request processing efficiency.
\item Managed AWS EC2 deployments, configured Nginx reverse proxies, and resolved production bottlenecks to ensure 99.9\% uptime.
\end{itemize}

\section*{Projects}

\textbf{\href{https://github.com/ShivSarwade/Griffion}{Griffion} -- Identity \& Authentication Service | Node.js, React.js, MongoDB, Redis}

\begin{itemize}[leftmargin=*]
    \item Developed a modular authentication microservice featuring JWT rotation, refresh token mechanisms, and secure session management.
    \item Optimized MongoDB database schemas and implemented caching strategies to minimize query overhead and improve authorization latency by 30\%.
    \item Built robust backend REST APIs and secure frontend workflows with protected routing, accelerating time-to-market for new internal tools.
\end{itemize}

\textbf{\href{https://github.com/ShivSarwade/JobJet}{JobJet} -- Full-Stack Job Portal | Python, React.js, Node.js, PostgreSQL}

\begin{itemize}[leftmargin=*]
    \item Engineered a scalable job-matching engine using Python with optimized string search and sorting algorithms for handling large datasets.
    \item Designed a responsive, component-driven frontend architecture using React.js and Tailwind CSS for seamless recruiter-candidate interactions.
    \item Created backend REST APIs using Node.js for application tracking, secure file uploads (resumes), and user profile management.
\end{itemize}

\textbf{\href{https://github.com/ShivSarwade/TICKETIFY}{TICKETIFY} -- Event Management System | React Native, Node.js, MongoDB}

\begin{itemize}[leftmargin=*]
    \item Engineered a highly available backend for a cross-platform event application, supporting high-concurrency ticket booking and real-time attendee synchronization.
    \item Implemented secure QR-based ticket validation and developed REST APIs to ensure reliable, low-latency event check-in operations under heavy load.
\end{itemize}

\section*{Awards \& Certifications}

\begin{itemize}[leftmargin=*]
   \item Secured 1st Rank in college during Bachelor’s degree graduation (BBA-CA / BCA) with a CGPA of 9.60/10 (Grade: O).
\end{itemize}

\section*{Education}

\textbf{Master of Computer Applications (MCA)} \hfill External, Expected: June 2027\\
Savitribai Phule Pune University (SPPU)\\
CGPA: 8.96 

\vspace{4pt} 

\textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
Savitribai Phule Pune University (SPPU)\\
CGPA: 9.60 / 10

\vspace{4pt} 

\textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022\\
A.S.D.B. Dadawala Junior College\\
Percentage: 87.50\%

\vspace{4pt} 

\textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020\\
V.P.S. Sheth Hiralal Saraf Prashala (S.H.S.P.)\\
Percentage: 88.20\%

\end{document}
