    \documentclass[a4paper,10pt]{article}

    % --- TIMES NEW ROMAN & ATS ENCODING ---
    \usepackage[T1]{fontenc}
    \usepackage{times}

    \usepackage[a4paper,margin=0.30in]{geometry}
    \usepackage{enumitem}
    \usepackage{titlesec}
    \usepackage[hidelinks]{hyperref}

    % Clean, tight spacing for section headings
    \titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
    \titlespacing*{\section}{0pt}{5pt}{3pt}

    % Globally reduce itemize vertical heights (pointers height reduction)
    \setlist[itemize]{
        noitemsep,
        topsep=1pt,
        parsep=0pt,
        partopsep=0pt,
        itemsep=1.5pt
    }

    \setlength{\parindent}{0pt}

    \begin{document}
    \pagestyle{empty}

    \begin{center}
        {\LARGE \textbf{SHIV SANTOSH SARWADE}}\\
        Frontend Software Developer - AI/LLM Specialization\\[4pt]
        +91-7620876612 \quad
        \href{mailto:shiv.s.sarwade@gmail.com}{shiv.s.sarwade@gmail.com} \quad
        \href{https://linkedin.com/in/shiv-sarwade}{linkedin.com/in/shiv-sarwade} \quad
        \href{https://github.com/ShivSarwade}{github.com/ShivSarwade}
    \end{center}

    \section*{Summary}

    Frontend-focused Software Engineer with 1+ year of experience building React.js and Next.js applications with emphasis on performance, reusable component architecture, and scalable frontend development. Specialized in AI-powered Document Cloud Web components with expertise in RAG systems, embeddings, and LLM integration. Experienced in REST API integration, state management, and delivering production-ready user interfaces. Proficient in prompt engineering, vector database workflows, and AI output evaluation techniques.

    \section*{Skills}

    \textbf{Frontend:} JavaScript (ES6+), TypeScript, React.js, Next.js, Redux Toolkit, GSAP, Framer Motion, Tailwind CSS, ShadCN, HTML5, CSS3\\
    \textbf{AI/LLM Technologies:} Retrieval-Augmented Generation (RAG), Vector Databases, Embeddings for Semantic Search, Prompt Engineering, AI Output Evaluation, Structured Metrics \& Feedback\\
    \textbf{Backend \& APIs:} Node.js, Express.js, REST APIs, JWT Authentication, RBAC\\
    \textbf{Databases:} PostgreSQL, MongoDB, Vector Databases, DBMS\\
    \textbf{Programming \& CS Fundamentals:} Python, TypeScript, Data Structures \& Algorithms, System Design, Computer Networking\\
    \textbf{Tools \& Platforms:} AWS EC2, Git, Linux, Postman, Nginx

    \section*{Experience}

    \textbf{Senior Frontend Software Developer} \hfill May 2025 -- Present\\
    Adobe Document Cloud, San Jose\\
    \textit{Tools Used: React.js, TypeScript, Node.js, RAG Systems, Vector Databases}

    
\begin{itemize}[leftmargin=*]
    \item Develop and implement software solutions for Document Cloud Web components, ensuring flawless and world-class quality across all deliverables.
    
    \item Add new features and fix bugs for various Document Cloud Web components using React.js and TypeScript with emphasis on performance and maintainability.
    
    \item Lead by collaborating with peers, mentoring junior team members, and building partnerships with key collaborators to achieve shared objectives.
    
    \item Collaborate with cross-functional teams to craft, develop, and deliver new features and improvements leveraging AI/LLM technologies.
    
    \item Write clean, maintainable, and efficient code, adhering strictly to coding standards and best practices.
    
    \item Participate in code reviews to ensure the quality and functionality of software across the team.
    
    \item Troubleshoot and debug software issues, providing robust solutions using advanced debugging and RAG-based context retrieval techniques.
    
    \item Continuously evaluate and improve the performance, scalability, and security of software using structured metrics and feedback loops.
    
    \item Implement RAG (Retrieval-Augmented Generation) systems for semantic search and context retrieval within Document Cloud platforms.
    
    \item Develop embedding-based features for semantic understanding and intelligent document processing workflows.
\end{itemize}


    \section*{Projects}

\textbf{Griffion -- Authentication Starter Kit | Next.js, Node.js, MongoDB, JWT}

\begin{itemize}[leftmargin=*]
    \item Built a reusable authentication starter kit providing pre-configured frontend and backend architecture for rapid application development.
    
    \item Implemented complete authentication workflows including JWT rotation, refresh token handling, RBAC, protected routes, and session management.
    
    \item Reduced repetitive setup effort by providing production-ready authentication infrastructure, enabling developers to focus primarily on business logic and UI development.
\end{itemize}

\textbf{JobJet -- Job Portal Platform | React.js, Tailwind CSS, Node.js, Express.js}

\begin{itemize}[leftmargin=*]
    \item Built a full-stack job portal platform supporting job listings, application workflows, user authentication, and recruiter-candidate interactions.
    
    \item Developed responsive frontend interfaces with structured state management and REST API integration for jobs, applications, and user workflows.
    
    \item Designed backend APIs with authentication, file uploads, validation, and role-based access handling using Node.js and Express.js.
\end{itemize}

\textbf{TICKETIFY -- Event Management Platform | React Native, Node.js}

\begin{itemize}[leftmargin=*]
    \item Built a cross-platform event management application supporting ticket booking, attendee management, and real-time event workflows.
    
    \item Implemented QR-based ticket validation and real-time attendee synchronization for faster and more reliable event check-in operations.
    
    \item Developed reusable mobile UI components and backend APIs to support scalable ticketing and event management workflows.
\end{itemize}
    \section*{Awards \& Certifications}

    \begin{itemize}[leftmargin=*]
        \item Secured 1st Rank in college during Bachelor's degree graduation (BBA-CA / BCA) with an outstanding CGPA of 9.60/10.
    \end{itemize}

    \section*{Education}

    \textbf{Master of Computer Applications (MCA)} \hfill Expected: June 2027\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 8.96 

    \vspace{4pt} 

    \textbf{Bachelor of Business Administration in Computer Applications (BBA-CA / BCA)} \hfill Graduated: 2025\\
    Savitribai Phule Pune University (SPPU)\\
    CGPA: 9.60 / 10

    \vspace{4pt} 

    \textbf{12th Class Higher Secondary Certification (H.S.C.)} \hfill 2021 -- 2022\\
    A.S.D.B. Dadawala Junior College\\
    Percentage: 87.50\%

    \vspace{4pt} 

    \textbf{10th Class Secondary School Certification (S.S.C.)} \hfill 2019 -- 2020\\
    V.P.S. Sheth Hiralal Saraf Prashala (S.H.S.P.)\\
    Percentage: 88.20\%

    \end{document}